\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-09 paper/main.tex
updating macro numbugs

%% macros
\newcommand{\Fix}[1]{\textbf{[[}\textcolor{red}{#1}\textbf{]]}}
\newcommand{\tname}{BugsInDLLs}
\newcommand{\jax}{JAX}
\newcommand{\torch}{PyTorch}
\newcommand{\tf}{Tensorflow}
\newcommand{\numbugs}{115}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem, but the lack of a curated set of reproducible bugs in DLLs
  hinders credible evaluation of such techniques. We present \tname, a
  database of curated reproducible bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

\begin{table}
  \centering
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{lrrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c}{$\Sigma$} & 102 & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}

>>>>

%% macros
\newcommand{\Fix}[1]{\textbf{[[}\textcolor{red}{#1}\textbf{]]}}
\newcommand{\tname}{BugsInDLLs}
\newcommand{\jax}{JAX}
\newcommand{\torch}{PyTorch}
\newcommand{\tf}{Tensorflow}
\newcommand{\numbugs}{102}

@@

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \sloppy
  AI-enabled applications are prolific today. Deep Learning
  libraries~(DLLs), such as \torch{} and \tf{}, provide the building
  blocks for the AI components of these applications. As any piece of
  software, these libraries can be buggy.
  %% and those bugs can affect a
  %% great deal of applications using those libraries.
  An impressive number of bug-finding techniques to address this
  problem have been proposed, but the lack of a curated set of
  reproducible bugs in DLLs hinders credible evaluation of these
  techniques. We present \tname, a database of curated reproducible
  bugs to fill that gap.
  %% enable credible  evaluation of bug-finding DLL testing techniques.
  Our dataset currently consists of \numbugs{} environments to
  reproduce bugs across three popular DLL libraries, namely, \jax,
  \tf, and \torch.
\end{abstract}

@@

\begin{table}
  \centering
  \caption{Characterization of reproducible bugs from \tname.}
\begin{tabular}{lrrr}
  \toprule
  & \multirow{2}{*}{\#} &  \multicolumn{1}{c}{build}          &   \multicolumn{1}{c}{enviroment}  \\
  &   & release-nightly &  venv-docker  \\
  \cmidrule(lr){2-4}
  \jax{} & 44 & 43-1 &  43-1 \\
  \torch{} & 33 & 15-18 & 19-14 \\
  \tf{} & 25 & 24-1 & 25-0 \\
  \midrule
  \multicolumn{1}{c}{$\Sigma$} & \numbugs{} & 82-20 & 87-15 \\
  \bottomrule
\end{tabular}
\end{table}
